prolfqua - An R-package for Proteomics Differential Expression Analysis.

### 2022-05-05 inst/MyArticle/paper.Rmd
fix methods formula

When computing differences among two groups $a$ and $b$, we will use the group mean $\bar{a}$ estimated from the data or the detection limit $a_d$ if no observations are present in the group. If for instance there are no observations in group $b$, then, $\Delta_{a,b} = \bar{a} - b_{dl}$ if $a > b_{dl}$ or $\Delta = 0$ if $a < b_{dl}$.

>>>>

When computing differences among two groups $a$ and $b$, we will use the group mean $\bar{a}$ estimated from the data or the detection limit $a_d$ if no observations are present in the group. If for instance there are no observations in group $b$, then, $\Delta_{a,b} = \bar{a} - b_{dl}$ if $\bar{a} > b_{dl}$ or $\Delta_{a,b} = 0$ if $\bar{a} < b_{dl}$.
